\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-02-18 main.tex
new format

\documentclass{acm_proc_article-sp}
%\documentclass[10pt, conference, compsocconf]{IEEEtran}

% From ASIACCS'13 CFP
% Submissions must be written in English, and must be at most 10 pages
% excluding the bibliography and well-marked appendices, and at most
% 12 pages overall.

@@

\title{Crossing Origins by Crossing Formats}

@@

The first steps in exploiting formats in the context of the web have
been taken by researchers. Two noteworthy examples are GIFAR~\cite{Brandis:GIFAR} and
cross-origin CSS attacks~\cite{Huang+:CCS10} (Section~\ref{sec:related}
discusses further related work). 
%
GIFAR is based on polyglots that combine the GIF and JAR (Java
archive) formats. The former is used as benign and the latter as
malicious to bypass SOP.
%
Cross-origin CSS attacks inject fragments of CSS code into an existing
web page to extract information from the existing web page.
%
The paper is the first to perform a systematic study of polyglot
attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content smuggling attacks.

@@

\paragraph{Contributions} The paper makes the following contributions:
\begin{itemize}
\vspace*{-.6cm}
\item Identification of polyglot attacks, a new breed of attacks for
  crossing origins by crossing formats;
\vspace*{-.2cm}
\item Characterization of the necessary ingredients for polyglot attacks
\vspace*{-.2cm}
\item Highlighting the PDF format as a particularly exposed format for
  polyglot attacks;
\vspace*{-.2cm}
\item Novel confidentiality and integrity attack vectors, based on syntax 
  injection and content smuggling;
\vspace*{-.2cm}
\item Evaluation of the current filtering mechanisms, browsers, and PDF
  filters for vulnerabilities; and
\vspace*{-.2cm}
\item Mitigation for the server, client, and PDF readers.
\end{itemize}

@@

While these articles document known instances of polyglot attacks, the attack 
method has up until now never been generalized. 
\todo{Is this a good place? is it a good way to say it?}
%
Two attacker-centric components require special attention; the infiltration of 
an origin, i.e. the attack vector, and the exploitation of an infiltrated origin, i.e. the payload.
%In this situation, the same-origin policy is intended to prevent cross-origin 
%interaction.

>>>>

%\documentclass{acm_proc_article-sp}
%\documentclass[10pt, conference, compsocconf]{IEEEtran}

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Polyglots : Crossing Origins by Crossing Formats}

@@

@@

The first steps in exploiting formats in the context of the web have
been taken by researchers. Two noteworthy examples are GIFAR~\cite{Brandis:GIFAR} and
cross-origin CSS attacks~\cite{Huang+:CCS10} (Section~\ref{sec:related}
discusses further related work). 
%
GIFAR is based on polyglots that combine the GIF and JAR (Java
archive) formats. The former is used as benign and the latter as
malicious to bypass SOP.
%
Cross-origin CSS attacks inject fragments of CSS code into an existing
web page to extract information from the existing web page.

\paragraph{Generalizing polyglots} 
The paper is the first to perform a generalization and systematic study of polyglot
attacks.
We identify the necessary ingredients for polyglot attacks.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins.

\paragraph{PDF polyglots} 
Having identified PDF as a particularly dangerous format, we perform
a novel in-depth study of
PDF-based injection and content smuggling attacks. 
Our findings expose new attack vectors, which we demonstrate both
conceptually and by a proof-of-concept web pages.

@@

%%% removed it - it repets what we already say above
% \paragraph{Contributions} The paper makes the following contributions:
% \begin{itemize}
% \vspace*{-.6cm}
% \item Identification of polyglot attacks, a new breed of attacks for
%   crossing origins by crossing formats;
% \vspace*{-.2cm}
% \item Characterization of the necessary ingredients for polyglot attacks
% \vspace*{-.2cm}
% \item Highlighting the PDF format as a particularly exposed format for
%   polyglot attacks;
% \vspace*{-.2cm}
% \item Novel confidentiality and integrity attack vectors, based on syntax 
%   injection and content smuggling;
% \vspace*{-.2cm}
% \item Evaluation of the current filtering mechanisms, browsers, and PDF
%   filters for vulnerabilities; and
% \vspace*{-.2cm}
% \item Mitigation for the server, client, and PDF readers.
% \end{itemize}

@@

While these articles document known instances of polyglot attacks, the attack 
method has not been generalized until this paper.
%
Two attacker-centric components require special attention; the infiltration of 
an origin, i.e. the attack vector, and the exploitation of an infiltrated origin, i.e. the payload.
%In this situation, the same-origin policy is intended to prevent cross-origin 
%interaction.
